Revisiting divisible, injective and flabby abelian groups from a constructive point of view

### 2022-09-26 slides-fischbachau2022.tex
Honouring Ada Lovelace
More work on slides

{\usebackgroundtemplate{\begin{minipage}{\paperwidth}\vspace*{5.95cm}\includegraphics[width=\paperwidth]{fr1-lighter}\end{minipage}}
\begin{frame}{}
  \textbf{Thm.}
  For every number~$n \in \NN$, there is a prime larger than~$n$.

@@

  {\centering\emph{``Every theorem has a computable witness.''}\par}
\end{frame}}

@@

    There are instances of~\badbox{\textsc{lem}} which HA does not prove.
    \bigskip

@@

    If HA proves~$\forall x\?N\_ \exists y\?N\_ \varphi(x,y)$,
    then there exists a function $f_0 : \NN \to \NN$ which is \hil{higher
    primitive recursive} such that for all~$x_0 \in \NN$, HA proves
    $\varphi(\underline{x_0}, \underline{f_0(x_0)})$.
  \end{enumerate}
\end{frame}

>>>>

{\usebackgroundtemplate{\begin{minipage}{\paperwidth}\vspace*{5.95cm}\includegraphics[width=\paperwidth]{fr1-lighter}\end{minipage}}
\begin{frame}{}
  \medskip
  \textbf{Thm.}
  For every number~$n \in \NN$, there is a prime larger than~$n$.

@@

  {\centering\emph{``Every theorem has a computable* witness.''} \\ \scriptsize
  * with monadic side effects\par}
\end{frame}}

% \includegraphics[width=3cm]{lovelace-babbage}
% \includegraphics[width=3cm]{first-program}
\addtocounter{framenumber}{-1}
{\usebackgroundtemplate{\begin{minipage}{\paperwidth}\includegraphics[height=\paperheight,valign=t]{ada-lovelace}\includegraphics[width=8cm,valign=t]{first-program}\end{minipage}}
\begin{frame}[plain]
  \vspace*{6cm}\hspace*{6cm}\begin{minipage}{4.7cm}
    \huge\hil{Ada Lovelace},

    \Large
    the world's first \\
    computer programmer
    \medskip

    * 1815 \ \ † 1852
  \end{minipage}
\end{frame}}

@@

    There are instances of~\badbox{\textsc{lem}} which HA does not prove,
    such as ``every Turing machine terminates or does not terminate''.
    \bigskip

@@

    If HA proves~$\forall x\?N\_ \exists y\?N\_ \varphi(x,y)$,
    then there exists a \hil{higher primitive recursive} function $f_0 : \NN
    \to \NN$ such that for all~$x_0 \in \NN$, HA proves
    $\varphi(\underline{x_0}, \underline{f_0(x_0)})$.
  \end{enumerate}
\end{frame}
